---
title: "Homework 1"
output:   
  github_document:
---

## Load packages
```{r, eval = FALSE}
library(tidyverse)
```


## Problem 1 

Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code. In your discussion, please include:

* the data in this dataset, including names / values of important variables
* the size of the dataset (using nrow and ncol)
* the mean flipper length
```{r}
data("penguins", package = "palmerpenguins")

nrow(penguins)
ncol(penguins)
# Total of 344 observations with 8 variables

head(penguins)
# Important variables include: species, body_mass_g, sex, year, flipper_length_mm

mean(penguins$flipper_length_mm, na.rm = TRUE)
# mean flipper length in mm: 200.9152

penguin_scatter <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point() +
  xlab("Bill Length (mm)") +
  ylab("Flipper Length (mm)")
ggsave("penguin_scatter_plot.pdf", plot = penguin_scatter)
```

## Problem 2

Create a data frame comprised of:

* random sample of size 10 from a standard Normal distribution
* logical vector indicating whether elements of the sample are greater than 0
* character vector of length 10
* factor vector of length 10, with 3 different factor “levels”

```{r}

```
