---
title: "Homework 1"
output:   
  github_document
---

## Load packages
```{r, echo = FALSE}
library(tidyverse)
```


## Problem 1 

Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code. In your discussion, please include...

* the data in this dataset, including names / values of important variables
* the size of the dataset (using nrow and ncol)
* the mean flipper length
```{r, collapse = TRUE}
data("penguins", package = "palmerpenguins")

# Total of 344 observations with 8 variables
nrow(penguins)
ncol(penguins)

# Important variables include: species, body_mass_g, sex, year, flipper_length_mm
head(penguins)

# mean flipper length in mm: 200.9152
mean(penguins$flipper_length_mm, na.rm = TRUE)

penguin_scatter <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point() +
  xlab("Bill Length (mm)") +
  ylab("Flipper Length (mm)")
ggsave("penguin_scatter_plot.pdf", plot = penguin_scatter)
```

## Problem 2

Create a data frame comprised of...

* random sample of size 10 from a standard Normal distribution
* logical vector indicating whether elements of the sample are greater than 0
* character vector of length 10
* factor vector of length 10, with 3 different factor “levels”

```{r}
set.seed(1)

df <- tibble(
  norm = rnorm(10, sd = 1),
  logic = c(FALSE, TRUE, FALSE, TRUE, TRUE, FALSE, TRUE, TRUE, TRUE, FALSE),
  char = c("hi", "my", "name", "is", "barry", "and", "i", "go", "to", "mailman"),
  factor = factor(c("blue", "yellow", "orange", "blue", "yellow", "orange", "blue", "yellow", "orange", "blue"))
  )
```


```{r, collapse = TRUE}
mean(df$norm)
mean(df$logic)
mean(df$char)
mean(df$factor)
```
We are able to take the mean of norm and logic.


```{r, eval = FALSE}
as.numeric(df$logic)
as.numeric(df$char)
as.numeric(df$factor)
```
We see the logical and factor variables become numerical variables while the character variable does not. We can see that in the background, R assigns and stores the logical and factor variables as integers. However, we are unable take the mean for the factor variable as R treats the integers as levels in a categorical variable.
