---
title: "Homework 1"
output:   
  github_document:
---

## Load packages
```{r, eval = FALSE}
library(tidyverse)
```


## Problem 1 
```{r}
data("penguins", package = "palmerpenguins")

nrow(penguins)
ncol(penguins)
# Total of 344 observations with 8 variables

head(penguins)
# Important variables include: species, body_mass_g, sex, year, flipper_length_mm

mean(penguins$flipper_length_mm, na.rm = TRUE)
# mean flipper length in mm: 200.9152

penguin_scatter <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("penguin_scatter_plot.pdf", plot = penguin_scatter)
```


## Data Import: CSVs

Let's import data using the 'readr' package

```{r}
litters_df <- read_csv('data/FAS_litters.csv')
litters_df <- janitor::clean_names(litters_df)
```


Look at table
```{r}
head(litters_df)
tail(litters_df)
skimr::skim(litters_df)
```


'read_csv' options..
```{r}
read_csv('data/FAS_litters.csv', na = c("", "NA", 999, 88), skip = 2)
?read_csv
# can also set variable type
```

## Other file formats

We need to read in an excel spreadsheet...
```{r}
mlb_df <- read_excel('data/mlb11.xlsx')
```

```{r, eval = FALSE}
view(mlb_df)
```

```{r}
lotr_words_df <-
  read_excel(
    'data/LotR_Words.xlsx',
    range = "B3:D6"
  )
```

## Still more formats ...

Read in SAS dataset
```{r}
pulse_df <- read_sas('data/public_pulse_data.sas7bdat')
```


## Data Export

```{r}
write_csv(lotr_words_df, file = 'data/results/lotr_words_df.csv')
```

## Why not base r???
```{r}
dont_do_this_df <- read.csv('data/FAS_litters.csv')
```
read.csv saves as data.frame, forces format but not able to change
ALWAYS use read_csv

## Git ignore
anything typed into file will be ignored and won't be uploaded to GitHub (i.e patient data)
make sure to save/commit/push


